The regularity of ODEs and thimble integrals \\ with respect to Borel summation \begin{draft}\textbf{[DRAFT]}\end{draft}

### 2024-06-27 exp-resurgence.tex
Mostly finalize "Thimble integrals in physics"

\end{revised} \begin{todo}Other treatments of the anharmonic oscillator: \cite{bender-wu}\cite[Appendix B]{aniceto2019primer}\cite[Section 2.5.3]{sternin1995borel}).\end{todo}

@@

\begin{revised}In wave optics, a thimble integral can arise when we adds up the secondary waves emanating from all the points along a wavefront~\cite{Fenyes-ihes-lecture}. For example, the Airy integral approximates the sum of the secondary waves coming from a wavefront with an inflection point~\begin{todo}[``the mathematical physics of rainbows and glories'']\end{todo}.\end{revised} \begin{todo}\textbf{A} [Mention Voros, and maybe Knoll--Schaeffer?]\end{todo} \begin{revised}In the path integral picture of quantum mechanics, which draws inspiration from wave optics,\end{revised} infinite-dimensional \begin{revised}thimble integrals\end{revised} are supposed to give the expectation values of observable quantities. In this context, \begin{revised}the integral's formal asymptotic expansion is often better-defined than the integral itself, so physicists use Borel summation, resurgence, and related techniques to assign the integral a value.\end{revised}
For instance, in the two-dimensional, $\mathcal{N}=2$ supersymmetric QFTs given by Landau--Ginzburg theories, Cecotti and Vafa showed that instantons can be computed using Picard--Lefschetz formulas. Indeed, the so called wall-crossing phenomenon is equivalent to Stokes phenomenon for thimble integrals~\cite{Cecotti:1992rm}.
Similarly, in complex Chern--Simons theory, the path integral can be studied by decomposing it into thimble integrals and then arguing as in finite dimesion~\cite{gukov-marino-purtrov-resurgence,Witten}. Other examples can be found in~\cite{costin_kruskal,Garoufalidis--CS,GTM--CS,GGM,dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua,Berry_Howls,Berry1991,Howls97,Howls,pham1988resurgence,Unsal--resurgence-gauge}.
\begin{todo}[\textbf{V} Is it true that all thimble integrals describes instantions? Can we have (higher dimensional) thimble integrals describing renormalons?]\end{todo}

@@

The Poincar\'{e} algorithm, as discussed in Section~\ref{sec:asympt-AL} picks out a frame in the \begin{draft}formal solutions\end{draft} \begin{todo}space of formal trans-series solutions [wrong: formal integral is not a trans-series because of direction conflict; say in footnote what the space is]\end{todo} of equation~\eqref{eqn:reg-mod-bessel-AL}. The frame is generated by $1$-Gevrey trans-monomial solutions of the form $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$, with $\tilde{W}_j \in \C\llbracket z^{-1} \rrbracket_1$. Reprising the proof of Theorem~\ref{thm:summability_ODE}, we will show that these solutions are Borel summable, and their Borel sums generate the same frame as $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$.

>>>>

 \begin{todo}Other treatments of the anharmonic oscillator: \cite{bender-wu}\cite[Appendix B]{aniceto2019primer}\cite[Section 2.5.3]{sternin1995borel}).\end{todo}

@@

In wave optics, a thimble integral can arise when we adds up the secondary waves emanating from all the points along a wavefront~\cite{Fenyes-ihes-lecture}. For example, the Airy integral approximates the sum of the secondary waves coming from a wavefront with an inflection point~\begin{todo}[``the mathematical physics of rainbows and glories'']\end{todo}. \begin{todo}The formalism of wave optics can also be applied to the scattering of quantum particles---for example, in the ``nuclear optical model'' [Knoll--Schaeffer]. [This inspired Voros's work in ``The return of the quartic oscillator'']\end{todo} In the path integral picture of quantum mechanics, which draws inspiration from wave optics, infinite-dimensional thimble integrals are supposed to give the expectation values of observable quantities. In this context, the integral's formal asymptotic expansion is often better-defined than the integral itself, so physicists use Borel summation, resurgence, and related techniques to assign the integral a value. For instance, in the two-dimensional, $\mathcal{N}=2$ supersymmetric QFTs given by Landau--Ginzburg theories, Cecotti and Vafa showed that instantons can be computed using Picard--Lefschetz formulas. Indeed, the so called wall-crossing phenomenon is equivalent to Stokes phenomenon for thimble integrals~\cite{Cecotti:1992rm}. Similarly, in complex Chern--Simons theory, the path integral can be studied by decomposing it into thimble integrals and then arguing as in finite dimesion~\cite{gukov-marino-purtrov-resurgence,Witten}. Other examples can be found in~\cite{costin_kruskal,Garoufalidis--CS,GTM--CS,GGM,dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua,Berry_Howls,Berry1991,Howls97,Howls,pham1988resurgence,Unsal--resurgence-gauge}. \begin{todo}[\textbf{V} Is it true that all thimble integrals describes instantions? Can we have (higher dimensional) thimble integrals describing renormalons?]\end{todo}

@@

The Poincar\'{e} algorithm, as discussed in Section~\ref{sec:asympt-AL} picks out a frame in a space of formal solutions of equation~\eqref{eqn:reg-mod-bessel-AL}. The frame is generated by $1$-Gevrey trans-monomial solutions of the form $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$, with $\tilde{W}_j \in \C\llbracket z^{-1} \rrbracket_1$. Reprising the proof of Theorem~\ref{thm:summability_ODE}, we will show that these solutions are Borel summable, and their Borel sums generate the same frame as $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$.
